Dual host-parasite transcriptomes of apicomplexan Eimeria falciformis and its natural mouse host

### 2016-07-22 figuresANDmanuscript/manuscriptBMCformat/manuscript_rnaseq.tex
Manuscript getting into results section - numbers added

The number of sequencing reads obtained for individual replicates
ranged between 111111 (samply NMRIxyz) and 222222 (NMRIwyv).

As samples and idividual replicates were sequenced in batches to
different depth and using different instrumentation (see additional
file 1 %%{or include sequencing even in Table 1?
) we performed quality controls confirming the abscence of batch
effects influencing analysis and quality of our results (additional
file xyc).

@@

A maximum of 75\% (sample NMRIaaga) and a minimum of 0.01\% (sample
NMRIagag) of mapped reads could be assigened to the
\textit{E. falciformis} genome in samples considered infected. We
excluded samples NMRI\_1st\_3dpi\_rep1 and NMRI\_2nd\_5dpi\_rep1 due
to an exptremely low parasite contribution to the overall
transcriptome. Technically this made it possible to obtain read counts
following negative bionmial distributions after normalization between
samples (see adddtional file x). Judging from their mRNA output those
samples can be considered non-infected.On the other end of the
spectruem this means that at 7dpi the majority of mRNA originated from
the parasite as opposed to the host transcriptome (Figure 1).

@@

We selected mouse
%%% This is from methods but all the results should be presented here:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	NUMBER OF GENES DIFFERENT IN DIFFERENT COMPARISONS	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{mRNA abundance differences between different experimental groups}
\setlength{\tabcolsep}{8pt}
\begin{table}[H]
\small
\begin{center}
\caption{mRNA abundance differences between different experimental groups.}
%\label{tab:table3}
\begin{tabular}{*3l}    \toprule
\textit{Day post infection} & \textit{Ef} genes different & Mouse genes different \\ 
	\textit{comparisons} 	    & (FDR$\leq$0.01) &  (FDR$\leq$0.01/0.05) \\ \midrule
	NMRI 0 vs NMRI 3		& NA   & 274 \\
	NMRI 0 vs NMRI 5		& NA   & 1736 \\
	NMRI 0 vs NMRI 7		& NA   & 2802 \\
	NMRI 3 vs NMRI 5     		& 111  & 1 \\
	NMRI 3 vs NMRI 7  		& 1385 & 1407 \\ 
	NMRI 5 vs NMRI 7  		& 1895 & 873 \\ 
	C57BL/6 0 vs C57BL/6 5		& NA	& 914 \\
	Rag1-/- 0 vs Rag1-/- 5		& NA	& 45 \\ \midrule
\textit{Day post infection,} & 		 & 		 \\ 
\textit{parasite relevant comparisons} 	    & 		&  \\ \midrule
	Oocysts vs NMRI 3  	& 3310 & NA \\  
	Oocysts vs NMRI 5	& 3605 & NA \\ 
	Oocysts vs NMRI 7	& 3085 & NA \\ 
	Oocysts vs sporozoites  & 3421 & NA \\
	Sporozoites vs NMRI 3 	& 1663 & NA \\
	Sporozoites vs NMRI 5 	& 1605 & NA \\
	Sporozoites vs NMRI 7 	& 2473 & NA \\ \midrule
\textit{First and second infection} & 		 & 	 \\ 
\textit{comparisons} 	    & 		& 	\\ \midrule
	NMRI 3 1st vs NMRI 3 2nd  	& 0  & 5 \\
	NMRI 5 1st vs NMRI 5 2nd  	& 0  & 1 \\
	NMRI 7 1st vs NMRI 7 2nd  	& 0  & 902 \\
	C57BL/6 1st vs C57BL/6 2nd (day 5) & 0 &  mouse \\
	Rag1-/- 1st vs Rag1-/- 2nd (day 5) & 0 & mouse  \\ \midrule
\textit{Mouse strain comparisons} & 		 & 	 \\ \midrule
	NMRI vs C57BL/6 		& 22 	& NA* \\		
	NMRI vs Rag1-/-     		& 0 & NA* 	\\
	C57BL/6 vs Rag1-/-  		& 0   & 356 	\\ \midrule
\bottomrule
	\hline
\end{tabular}
\end{center}
\end{table}

>>>>

The number of sequencing reads obtained for individual replicates
ranged from 21,517,055 (sample NMRI\_sporozoites\_rep2) to 593,396,312
(NMRI\_2ndInf\_5dpi\_rep1).

As samples and idividual replicates were sequenced in batches to
different depth and using different instrumentation (Table 1) we
performed quality controls confirming the abscence of batch effects
influencing analysis and quality of our results (additional file xyc).

@@

A maximum of 86\% (sample NMRI\_1stInf\_7dpi\_rep1) and a minimum of
0.0326\% (sample NMRI\_2ndInf\_3dpi\_rep2) of mapped reads could be
assigened to the \textit{E. falciformis} genome in samples considered
infected.

We excluded samples NMRI\_2nd\_3dpi\_rep1 and NMRI\_2nd\_5dpi\_rep2
due to an exptremely low parasite contribution to the overall
transcriptome. Technically this exclusion made it possible to obtain
read counts in agreement with a negative bionmial distributions (see
adddtional file x). Judging from their mRNA output those samples can
be considered non-infected, as both samples occured in a challenge
infection we assume that the infection was cleard or reduced to a
non-detectable output in those animmals.

On the other end of the spectrum mice not previously immunized
featured an mRNA ``holo-transcriptome'' at 7dpi with the majority of
mRNA originating from the parasite as opposed to the host (Figure 1).

@@

We selected all mouse genes differently expressed (FDR<1\%) between
uinfected and any of the infected samples.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	NUMBER OF GENES DIFFERENT IN DIFFERENT COMPARISONS	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% I like this table. Looks good and transprorts the right kind of
%% information

\clearpage
\section{mRNA abundance differences between different experimental groups}
\setlength{\tabcolsep}{8pt}
\begin{table}[H]
\small
\begin{center}
\caption{mRNA abundance differences between different experimental groups.}
%\label{tab:table3}
\begin{tabular}{*3l}    \toprule
\textit{Day post infection} & \textit{Ef} genes different & Mouse genes different \\ 
	\textit{comparisons} 	    & (FDR$\leq$1\%) &  (FDR$\leq$1\%/5\%) \\ \midrule
	NMRI 0 vs NMRI 3		& NA   & 274 \\
	NMRI 0 vs NMRI 5		& NA   & 1736 \\
	NMRI 0 vs NMRI 7		& NA   & 2802 \\
	NMRI 3 vs NMRI 5     		& 111  & 1 \\
	NMRI 3 vs NMRI 7  		& 1385 & 1407 \\ 
	NMRI 5 vs NMRI 7  		& 1895 & 873 \\ 
	C57BL/6 0 vs C57BL/6 5		& NA	& 914 \\
	Rag1-/- 0 vs Rag1-/- 5		& NA	& 45 \\ \midrule
\textit{Day post infection,} & 		 & 		 \\ 
\textit{parasite relevant comparisons} 	    & 		&  \\ \midrule
	Oocysts vs NMRI 3  	& 3310 & NA \\  
	Oocysts vs NMRI 5	& 3605 & NA \\ 
	Oocysts vs NMRI 7	& 3085 & NA \\ 
	Oocysts vs sporozoites  & 3421 & NA \\
	Sporozoites vs NMRI 3 	& 1663 & NA \\
	Sporozoites vs NMRI 5 	& 1605 & NA \\
	Sporozoites vs NMRI 7 	& 2473 & NA \\ \midrule
\textit{First and second infection} & 		 & 	 \\ 
\textit{comparisons} 	    & 		& 	\\ \midrule
	NMRI 3 1st vs NMRI 3 2nd  	& 0  & 5 \\
	NMRI 5 1st vs NMRI 5 2nd  	& 0  & 1 \\
	NMRI 7 1st vs NMRI 7 2nd  	& 0  & 902 \\
	C57BL/6 1st vs C57BL/6 2nd (day 5) & 0 &  mouse \\
	Rag1-/- 1st vs Rag1-/- 2nd (day 5) & 0 & mouse  \\ \midrule
\textit{Mouse strain comparisons} & 		 & 	 \\ \midrule
	NMRI vs C57BL/6 		& 22 	& NA* \\		
	NMRI vs Rag1-/-     		& 0 & NA* 	\\
	C57BL/6 vs Rag1-/-  		& 0   & 356 	\\ \midrule
\bottomrule
	\hline
\end{tabular}
\end{center}
\end{table}
